%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[8pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\def\labelitemi{--}

\usepackage{enumerate}
\usepackage{color}
\usepackage{url}
\usepackage{helvet} % Default font is the helvetica postscript font
% \usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

\name{Christopher A. Wood\\ \\} % Your name at the top

\address{{\bf Permanent Address} \\ 2000 Post St., Apt. 123 \\ San Francisco, CA 94115 } % Your address 1
%{\bf Contact Information} \\
\address{Phone: (315) 806-5939 \\ Email: woodc1@uci.edu \\ \url{www.christopher-wood.com}} % Your address 2

\begin{resume}

\vspace{-5pt}
\section{\centerline{EDUCATION}}

\vspace{8pt} % Gap between title and text

{\sl Doctor of Philosophy},
Computer Science \\
University of California Irvine, Irvine, CA \hfill 2013 - 2018 (expected) \\
Advisor: Dr. Gene Tsudik \\
GPA: 4.0/4.0

{\sl Master of Science}, Computer Science\\
Rochester Institute of Technology, Rochester, NY \hfill 2012 - 2013 \\
Advisor: Dr. Stanis{\l}aw Radziszowski \\
GPA: 4.0/4.0

{\sl Bachelor of Science}, Computer Science and Software Engineering\\
Rochester Institute of Technology, Rochester, NY \hfill 2008 - 2012 \\
GPA: 3.98/4.0 (Professional Field of Study GPA: 4.0/4.0)

\section{\centerline{SELECTED PUBLICATIONS}}

\begin{enumerate}[C-1.]

\item P. Bajorski, A. Kaminsky, M. Kurdziel, M. Lukowiak, S. Radziszowski, and C. Wood, ``Stochastic Analysis and Modeling of a Tree-Based Group Key Distribution Method in Tactical Wireless Networks,'' to appear in {\it Journal of Telecommunications System \& Management, Engineering Journals, OMICS Publishing Group}.

\item C. Ghali, G. Tsudik, C. A. Wood, E. Yeh, ``Practical Accounting in Content-Centric Networking,''  \emph{NOMS 2016, IEEE/IFIP Network Operations and Management Symposium}, April 25 - 29, 2016, Istanbul, Turkey.

\item G. Tusik, E. Uzun, and C. A. Wood, ``AC3N: An API and Service for Anonymous Communication in Content-Centric Networking,'' in \emph{Proceedings of CCNC 2016}, Las Vegas, NV, USA. January 2016.

\item M. Mosko and C. A. Wood, ``Secure Fragmentation for Content-Centric Networking,'' \emph{IEEE MASS 2015 Workshop on Content-Centric Networking (CCN 2015)}, Dallas, TX, USA. October 2015. {\color{red} (Best paper award winner)}

\item C. Ghali, M. A. Schlosberg, G. Tsudik, and C. A. Wood, ``Interest-Based Access Control for Information Centric Networks,'' in \emph{Proceedings of ICN 2015, the 2nd ACM Conference on Information Centric Networking}, San Francisco, CA, USA. September 2015.

\item C. Ghali, A. Narayanan, D. Oran, G. Tsudik, and C. A. Wood, ``Secure Fragmentation for Content-Centric Networks,'' \emph{NCA 2015, the 14th IEEE International Symposium on Network Computing and Applications}, Cambridge, MA, USA. September 2015.

\item C. A. Wood and J. Jacob, ``Characterization of Small Trees Based on their L(2,1)-Span,'' \emph{AKCE International Journal of Graphs and Combinatorics}, Volume 12, Issue 1, July 2015, Pages 26–31.

\item J. Kurihara, C. A. Wood, and E. Uzun, ``An Encryption-Based Access Control Framework for Content-Centric Networking,'' \emph{IFIP Networking 2015}, Toulouse, France. May 2015.

\item M. Lukowiak, S. Radziszowski, J. Vallino, C. Wood, ``Cybersecurity Education: Bridging the Gap between Hardware and Software Domains,'' {\it ACM Transactions on Computing Education}, 14(1) (2014).

\item C. A. Wood and E. Uzun, ``Flexible End-to-End Content Security in CCN,'' \emph{IEEE Consumer Communications and Networking Conference (CCNC 2014) Special Session: Information Centric Networking}, Las Vegas, Nevada. January 2014.

\end{enumerate}

% \vspace{0.2in} % Some whitespace between sections

\section{\centerline{SELECTED TALKS AND PRESENTATIONS}}

\vspace{18pt} % Gap between title and text

\begin{enumerate}[P-1.]

\item ``Efficient Security Bindings for Information Centric Networks,'' \emph{CCNxCon 2015, Palo Alto Research Center, Palo Alto, CA}. May 20, 2015.

\item ``Handling Trust Enforcement,'' presentation, \emph{CCNxCon 2015, Palo Alto Research Center, Palo Alto, CA}. May 20, 2015.

\item ``Digital Signatures and Implicit Certificates,'' guest lecture for Dr. Stanislaw Radziszowski's (CS@RIT), Crypto II course, May 5, 2015.

\item ``Secure Content Dissemination in Content Centric Networking,'' \emph{CCNxCon 2013, Palo Alto Research Center, Palo Alto, CA}. September 5, 2013.

%\item ``Cryptographic S-boxes,'' guest lecture for Dr. Stanislaw Radziszowski's (CS@RIT) Crypto II course, April 8, 2013.

\end{enumerate}
\vspace*{-16pt}

\vspace{0.2in} % Some whitespace between sections

\section{\centerline{RECENT PROFESSIONAL EXPERIENCE}}

\vspace{8pt} % Gap between title and text

{\sl Palo Alto Research Center} \hfill June 2014 - present \\
Computer Science Laboratory, Palo Alto, CA \hfill Network Software Development Engineer
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Develop the CCNx 1.0 software stack, libraries, and APIs.
\item Write IETF RFC drafts for various elements of the CCN protocol.
\end{itemize}

{\sl Palo Alto Research Center} \hfill July 2013 - September 2013 \\
Computer Science Laboratory, Palo Alto, CA \hfill Security and Privacy Research Intern
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Researched security and privacy aspects related to content-centric network (CCN).
\item Implemented the Green-Ateniese (pairing-based) and Chow-Weng-Yang-Deng (Schnorr- and ElGamal-based) Proxy Re-Encryption schemes in Java for use in a CCNx application.
\item Studied and tested various techniques for securing content.
\end{itemize}

{\sl Intel Corporation} \hfill June 2012 - August 2012 \\
Virtual \& Parallel Computing Group, Folsom, CA \hfill Graphics Software Engineer Intern
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed production features for tool that processes hardware specifications to generate web content and source code for VHDL and C/C++ testbeds.
\item Interacted with internal customers within the VPG to utilize debug tools and environments for architecture specification and post-silicon testing.
\end{itemize}

\vspace{-4pt}

\section{\centerline{RECENT ACADEMIC EXPERIENCE}}

\vspace{4pt} % Gap between title and text

{\sl Advanced Cryptography} \hfill May 5, 2015 \\
Guest Lecturer for Dr. Stanis{\l}aw Radziszowski (CS) \hfill (RIT)
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Lectured about digital signature algorithms, ElGamal and ECDSA batch verification techniques, standard public key infrastructures, and the OMC and ECQV implicit certificate schemes.
\end{itemize}

{\sl Hardware and Software Design with Cryptographic Applications} \hfill February 2011 - May 2013 \\
Teaching Assistant and Lecturer for Dr. Marcin Lukowiak (CE) \hfill (RIT)
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Developed and delivered lecture material on cryptography, embedded software optimization techniques, the Impulse C high-level synthesis tool, and AES cache timing attacks.
\end{itemize}

\vspace{-4pt}

\section{\centerline{HONORS AND ACTIVITIES}}

\vspace{16pt} % Reduce space between section title and contents

\begin{itemize} \itemsep -2pt
\item NSF GRFP fellowship recipient, 2014
\item RIT Honors Program, 2009 -- 2013
\item RIT Tau Beta Pi Engineering Honors Society, 2011 -- 2013
\item RIT Outstanding Undergraduate Student award, selected, Winter 2012
\item RIT Computer Science MS Student Delegate, selected, Winter 2012
\item Recipient of Golisano College Honors research assistantship stipend, Winter 2009/2010
\item Recipient of Golisano College Honors research assistantship stipend, Spring 2011
\item Recipient of RIT undergraduate research award stipend, Summer 2009
\item RIT Golisano College Dean's List, 2008 -- 2013
\end{itemize}

\end{resume}
\end{document}
