% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
\usepackage{multicol}
\usepackage{verbatim}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Christopher A. Wood}
% \address used twice to have two lines of address
\address{71-4 Lilac Drive, Rochester, NY 14620}
\address{caw4567@rit.edu - (315) 806-5939}

\begin{resume}
 
%\section{OBJECTIVE}       A position in the field of computer science research and development with a specific %focus on computer security, including elements of hardware/software co-design, applied cryptography, %operating system hardening and protection, and/or malware design and detection.
 
\section{EDUCATION} 
		{\sl Master of Science,} Computer Science, expected 08/2013 \\
		{\sl Bachelor of Science,} Software Engineering and Computer Science, expected 08/2013 \\
                Rochester Institute of Technology, Rochester, NY 
\vspace{0.005cm} 

                {\sl Concentrations}: Computational Mathematics and Computer Engineering \\
                {\sl Minors}: Mathematics and Writing Studies \\
	     	{\sl GPA}: 3.97/4.0 (Primary Field of Study GPA: 4.0/4.0) 
\vspace{0.005cm} 

		{\sl MS Thesis}: ``Optimal Representations of Cryptographically Significant Vectorial Boolean Functions'', expected 08/2013, under development.
\vspace{0.005cm} 

		{\sl Relevant coursework}: \\Algorithms, Data Communications and Networks, Intelligent Security Systems, Compiler Construction, Optimization Methods, Operating Systems, Programming Language Concepts, Computer Organization, Computer Science Theory, Number Theory, Graph Theory, Linear Algebra, Discrete Mathematics, Real-time and Embedded Systems, Performance Engineering of Real-time and Embedded Systems, Concurrent Systems, Software Formal Methods, Engineering of Software Subsystems, Software Architectures, Software Testing, Professional Communications, Technical Writing.

\section{PUBLICATIONS}
	\begin{enumerate}
	\item C. Wood and J. Jacob, "Forbidden Subtree Construction Techniques for Trees Under the $L(2,1)$-Labeling Problem on Trees," in preparation.
	\item C. Wood and J. Jacob, "Characterization Results for the $L(2,1)$-Labeling Problem on Trees," in preparation.
	\item P. Bajorski, A. Kaminsky, M. Kurdziel, M. Lukowiak, S. Radziszowski, and C. Wood, "Statistical Analysis and Modeling of a Tree-Based Group Key Distribution Method in Tactical Wireless Networks," submitted.
	\item M. Lukowiak, S. Radziszowski, J. Vallino, C. Wood, "Cybersecurity Education: Bridging the Gap between Hardware and Software Domains," submitted.
	\item M. Lukowiak, A. Meneely, S. Radziszowski, J. Vallino, and C. Wood, "Developing an Applied, Security-Oriented Computing Curriculum," In Proceedings of the ASEE 2012, San Antonio, Texas. June 2012.
	\item C. A. Wood, "Chaos-Based Symmetric Key Cryptosystems," In Proceedings of the 2011 International Conference on Security \& Management, Las Vegas, Nevada, USA. July 2011.
	\item C. A. Wood and R. K. Raj, "Keyloggers in Cybersecurity Education," In Proceedings of the 2010 International Conference on Security \& Management, Las Vegas, Nevada, USA. July 2010.
	\end{enumerate}

\section{INVITED \\TALKS}
	\begin{enumerate}
		\item C. Wood, “Characterization Results for the L(2,1)-Labeling Problem on Trees”, AMS Sectional Meeting, Rochester Institute of Technology, Rochester, NY, September, 22 2012.	
	\end{enumerate}

\section{POSTER\\PRESENTATIONS}
	\begin{enumerate}
		\item C. A. Wood, "Layered Driver Rootkit Detection on Microsoft Windows PCs", Poster Presentation, RIT Undergraduate Symposium, August 2009.
	\end{enumerate}

\section{RESEARCH\\EXPERIENCE}
	{\sl Secure Logging Schemes for Cloud-Based SaaS Architectures} \hfill   9/12 - present\\
	 Advisors: Dr. Rajenda K. Raj (RIT Computer Science Department) and Dr. Andy Meneely (RIT Software Engineering Department)
	\begin{itemize} \itemsep -2pt %reduce space between items
		\item Reconstructing a cloud-based secure logging architecture that leverages ciphertext-policy attribute based encryption (CP-ABE) for log file integrity.
		\item Conducting a literature survey on past and present secure logging architectures.
	\end{itemize}

	{\sl Keyboard Biometric-Based Continuous Authentication Schemes} \hfill   9/12 - present\\
	 Advisor: Dr. Leon Reznik (RIT Computer Science Department) 
	\begin{itemize} \itemsep -2pt %reduce space between items
		\item Implementing a real-time keyboard keylogger and feature extraction engine for use in continuous authentication schemes.
		\item Comparing classifiers based on dynamic free-form text input against those based on structured text-input.
		\item Conducting a survey on past and present keyboard-based biometric authentication schemes.
	\end{itemize}

	{\sl Wireless Ad-hoc Network Group Key Management} \hfill    5/11 - present\\
	Advisors: Dr. Stanis{\l}aw Radziszowski (RIT Computer Science Department), Dr. Marcin Lukowiak (RIT Computer Engineering Department), Dr. Peter Bajorski (RIT Graduate Statistics Department), Dr. Michael Kurdziel (Harris RF Communications Division)
	\begin{itemize} \itemsep -2pt %reduce space between items
	\item Focusing on a group key management protocols for wireless ad-hoc radio networks with constrained channel bandwidths and computational power.
	\item Exploring solutions based on public- and private-key cryptosystems with varying levels of pre-placed radio data for node authentication and key generation.
	\item Implementing network simulators in SMURPH/SIDE and NS3 to obtain empirical performance measurements for proposed protocols.
	\item Implementing a SPIN model to check the correctness of our protocol (i.e. its adherence to the specification).
	\item Developing a theoretical mathematical model to compare with quantitative performance metrics.
	\end{itemize}

	{\sl $L(2,1)$-Labeling Problem} \hfill   9/11 - 9/12\\
	 Advisor: Dr. Jobby Jacob (RIT School of Mathematical Sciences)
	\begin{itemize} \itemsep -2pt %reduce space between items
	\item Studied previous results from the $L(2,1)$-labeling problem on trees.
	\item Implemented a dynamic programming labeling algorithm to assist in the study of tree characterization.
	\item Developed tree construction algorithms that are capable of producing infinitely many trees $T$ with a label span of $(\Delta(T) + 2)$.
	\item Made progress in the complete $L(2,1)$ label span characterization of trees up to twenty vertices using the aforementioned labeling algorithm and nauty graph generation program.
	\item Briefly investigated the $L(2,1)$-labeling problem on cubic bipartite graphs.
	\end{itemize}

	{\sl Secure Operating System Design Principles} \hfill    3/11 - 6/11\\
	 Advisor: Dr. Rajenda K. Raj (RIT Department of Computer Science) 
	\begin{itemize} \itemsep -2pt %reduce space between items
	\item Researched secure operating system design principles at all levels of the software stack.
	\item Conducted case studies for a variety of popular operating systems with different purposes, including Microsoft Singularity, Chrome OS, Android (the entire stack), QNX, and Microsoft Azure.
	\item Began developing a primitive operating system, virtual machine, and programming language to explore the implementation aspects of secure systems.
	\end{itemize}

	{\sl Rootkit Design, Implementation, and Detection} \hfill    6/09 - 3/10\\
	 Advisor: Dr. Rajendra K. Raj (RIT Department of Computer Science) 
	\begin{itemize} \itemsep -2pt %reduce space between items
	\item Explored malware rootkits that targeted the Windows NT family of operating systems.
	\item Studied user-mode and kernel-mode rootkit implementations and state-of-the-art static and dynamic techniques.
	\item Developed a Windows NT filter driver in C to help determine the presence of keystroke-monitoring malware (targeted towards a specific rootkit implementation).
	\end{itemize}
 
\section{PROFESSIONAL \\EXPERIENCE} 
	 {\sl Intel Corporation, Virtual and Parallel Computing Group (VPG) } \hfill   6/12 - 8/12\\
                Graphics Software Engineer Intern \hfill Folsom, CA
                 \begin{itemize}  \itemsep -2pt %reduce space between itemsddd
                 \item Developed production features for language transformation software for hardware specifications to test platform source files.
		\item Interacted with internal customers within the VPG to utilize debug tools and environments for architecture specification and post-silicon testing.
		 \item Drove a large refactor of an existing system to make use of multiple design patterns, including the Factory, Decorator, and Adapter patterns.
                 \end{itemize} 
	
	{\sl L-3 Communications, Linkabit Division} \hfill 3/11 - 8/11\\
	      Software Engineer Intern \hfill Victor, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between itemssss
                 \item Designed and implemented a library and supporting drivers for the u-blox NEO5/6 GPS receiver to be driven by an Analog Devices Blackfin processor.
		\item Extended an existing FAT file system driver to add support for SD devices.
		\item Improved functionality of an existing CPLD design used to control the power supply in an embedded system.
		\item Responsible for managing an internal project build machine using Cruise Control and running Coverity static analysis tools on C/C++ projects to obtain defect reports.
                \end{itemize}

	{\sl Rochester Software Associates} \hfill 11/10 - 3/11\\
	      Software Engineer Intern \hfill Rochester, NY
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Led the design, development, and documentation efforts for a new printer job management application that would service any number of jobs from clients across the network.
		\item Tested and debugged an existing implementation of the LPD protocol.
                \end{itemize}

%	 {\sl RIT Honors Program} \hfill    3/11 - 6/11, 11/09 - 2/10, and 6/09 - 9/09\\
 %               Student Researcher \hfill Rochester, NY
  %               \begin{itemize}  \itemsep -2pt %reduce space between itemsddd
%		\item Extensively studied secure operating system design and implementation with a focus on %Chrome OS, Android, QNX, and Windows Azure
 %                \item Studied user-mode and kernel-mode rootkit implementation and detection techniques
%		\item Developed Windows NT filter driver in C to help determine the presence of %keystroke-%monitoring malware
%		\item Added TCP/IP support to keystroke-logging rootkit using the Transport Driver Interface in %C++
 %                \end{itemize} 

	  {\sl C Speed, LLC} \hfill   5/10 - 8/10\\
                Software Engineer Intern \hfill Liverpool, NY
                 \begin{itemize}  \itemsep -2pt %reduce space between itemsddd
                 \item Implemented embedded firmware features and test routines in C, C++, and Assembly for Coldfire V2 processors.
		\item Designed and implemented an internal manufacturing part supply management system.
                 \end{itemize} 

\section{TEACHING \\EXPERIENCE}
	{\sl RIT Software Engineering Department} \hfill   2/11 - present\\
                Teaching Assistant \hfill Rochester, NY
                 \begin{itemize}  \itemsep -2pt %reduce space between itemsddd
                 \item Helped design and teach a new course entitled "Hardware and Software Design with Cryptographic Applications".
		\item Developed lecture material on real-time and embedded software optimization techinques and the Impulse C high-level synthesis tool.
		\item Prepared and presented material on software application profiling and optimization techniques.
		\item Assisted students with weekly assignments and graded lab and project deliverables.
		\item Porting the AES cache timing attack on a Xilinx ML507 platform with MicroBlaze soft-core processor for student labs.
                 \end{itemize} 

	{\sl RIT Computer Science Department} \hfill    12/09 - present\\
	Computer Science I, II, and IV Lab Assistant \hfill Rochester, NY
	\begin{itemize} \itemsep -2pt %reduce space between items
	\item Run weekly lab meetings and problem solving sessions with brief lectures to cover weekly material.
	\item Hold four tutoring office hours per week to assist students in need.
	\item Grade weekly lab assignments and midterm examinations.
	\end{itemize}

\begin{comment}
	{\sl RIT Software Engineering Department} \hfill    1/12 - 5/12\\
	Data Structures and Algorithms Tutor \hfill Rochester, NY
	\begin{itemize} \itemsep -2pt %reduce space between items
	\item Provided personal assistance for students trying to understand the material tought in the course.
	\item Analyzed design and implementation decisions for course projects.
	\end{itemize}

{\sl RIT Computer Science Department} \hfill   9/10 - 3/11 \\
                Computer Organization Grader \hfill Rochester, NY
                 \begin{itemize}  \itemsep -2pt %reduce space between itemsddd
                 \item Graded weekly programming assignments and long-term projects with automated test programs and manual MIPS assembly inspection.
                 \item Assisted in grading of midterm and final examinations.
                 \end{itemize} 

\end{comment}

	{\sl RIT Software Engineering Department} \hfill    12/11 - 3/12\\
	Personal Software Engineering Teaching Assistant \hfill Rochester, NY
	\begin{itemize} \itemsep -2pt %reduce space between items
	\item Assisted students with in-class programming assignments and course projects.
	\item Graded student projects, including those based on the C and Ruby programming languages.
	\end{itemize}

	{\sl RIT Software Engineering Department} \hfill    9/11 - 12/11\\
	Engineering of Software Subsystems Teaching Assistant \hfill Rochester, NY
	\begin{itemize} \itemsep -2pt %reduce space between items
	\item Assisted students with in-class exercises and unit questions based on a subset of the design patterns taught during the course.
	\item Spent time with each student team to discuss course projects, including design decisions, application of design patterns, and alternatives considered.
	\item Graded course project implementations unit questions.
	\end{itemize}

\section{ACADEMIC AND \\ PERSONAL \\PROJECTS}             
	\begin{itemize}
	\item Replicating the published cache timing attack on LUT-based implementations of the Advanced Encryption Standard on an FPGA-based embedded system.
	\item Implemented a fully-compliant FTP client with a text-based interface in Java (approximately 2,000 lines of code). 
	%\item Led white-box testing efforts for a six-person team project that focused on functionality, acceptance, unit, stress, and load testing activities for TuxGuitar.
	\item Led the development effort for a four-person team that worked on a Kanban taskboard web application using Adobe Flex, Flash, BlazeDS, Hibernate, Jasper Reports, and Java (approximately 10,000 lines of code).
	%\item Medical Image Viewing System featuring image scrolling and multi-axis reconstructions of X-rays, CT scans, and MRIs in various file formats.
	\item Led team to develop a Java-based medical image viewing and reconstruction system featuring image scrolling and multi-axis reconstructions of X-ray, CT scan, and MRI images in various file formats (approximately 6,500 lines of code).
	%\item Led development for a 4-person team implementing a Java-based Point of Sale system that leveraged SQLite for as the main database for information persistence; performed unit, integration, regression, and system testing; held team meetings (approximately 5,000 lines of code).
	%\item Developed an abstract two-player game solver framework and AI in C++ (approximately 1,500 lines of code).
	%\item Implemented an AOL instant messenger and IRC chat program in Java (approximately 2,000 lines of code).
	\end{itemize}

\section{HONORS AND \\ AWARDS}
	\begin{itemize}
	\item Golisano College of Computing and Information Sciences (GCCIS) and RIT Honors Program, Member.
	\item RIT Tau Beta Pi Engineering Honors Society, Member.
	\item Student mentor for the FIRST LEGO League team hosted by RIT, 2009-2011.
	\item Recipient of GCCIS Honors research assistantship award for Winter 2009-2010 and Spring 2011.
	\item Recipient of RIT Undergraduate Research Award stipend for Summer 2009.
	\item Appointed to GCCIS Dean's List (Fall 2008 - present).
	%\item Society of Software Engineers at RIT, Member.
	\end{itemize}

\section{PERSONAL \\INTERESTS}
	\begin{itemize}
	\item Marathon finisher, full 42km Lake Placid Marathon, June 12, 2011, 4:29:15 completion time.
	\item Acoustic and electric guitar, 3 years.
	\end{itemize}

\end{resume}
\end{document}







